% \nocite{*}
\begin{thebibliography}{19}

\bibitem{first} Spellman PT, Sherlock G, Zhang M, Iyer V, Anders K, Eisen M, Brown
P, Botstein D, Futcher B: Comprehensive identification of cell
cycle-regulated genes of the yeast Saccharomyces cerevisiae
by microarray hybridization. Mol Biol Cell 1998, 9(12):3273-97.

\bibitem{second} Arbeitman M, Furlong E, Imam F, Johnson E, Null B, Baker B, Krasnow
M, Scott M, Davis R, White K: Gene expression during the life
cycle of Drosophila melanogaster. Science 2002, 297:2270-75.

\bibitem{third} Guillemin K, Salama N, Tompkins L, Falkow S: Cag pathogenicity
island-specific responses of gastric epithelial cells to Helicobacter pylori infection. Proc Natl Acad Sci USA 2002,
99:15136-15141

\bibitem{fourth} Guillemin K, Salama N, Tompkins L, Falkow S: Cag pathogenicity
island-specific responses of gastric epithelial cells to Helicobacter pylori infection. Proc Natl Acad Sci USA 2002,
99:15136-15141

\bibitem{hierarcial} Eisen MB, Spellman PT, Brown PO, Botstein D: Cluster analysis
and display of genome-wide expression patterns. PNAS 1998,
95(25):14863-14868.

\bibitem{knn} S T, Hughes JD, Campbell MJ, Cho RJ, Church GM: Systematic
determination of genetic network architecture. Nature Genetics 1999, 22(3):281-285.

\bibitem{som} Tamayo P, Slonim D, Mesirov J, Zhu Q, Kitareewan S, Dmitrovsky E,
Lander E, Golub T: Interpreting patterns of gene expression
with self organizing maps: Methods and applications to
hematopoietic differentiation. PNAS 1999, 96:2907-2912.

\bibitem{financial time} T
SAY
, R.S.
(2002)
Analysis of financial time series
, John Wiley \& Sons: New York. 

\bibitem{weather} Marc Saez et al. Relationship between Weather Temperature and Mortality: A Time Series Analysis Approach in Barcelona :  International Journal of Epidemiology, Volume 24, Issue 3, 1 June 1995, Pages 576–582, https://doi.org/10.1093/ije/24.3.576. 


\bibitem{STEM} Ernst J, Bar-Joseph Z. STEM: a tool for the analysis of short time series gene expression data. BMC Bioinformatics. 2006;7:191. doi:10.1186/1471-2105-7-191.

\bibitem{period} Alan Wee-Chung Liew \& Hong Yan. Reliable Detection of Short Periodic Gene Expression
Time Series Profiles in DNA Microarray Data. Proceedings of the 2009 IEEE International Conference on Systems, Man, and Cybernetics.

\bibitem{Coexp} Bhar A, Haubrock M, Mukhopadhyay A, Maulik U, Bandyopadhyay S, Wingender E. Coexpression and coregulation analysis of time-series gene expression data in estrogen-induced breast cancer cell. Algorithms for Molecular Biology: AMB. 2013;8:9. doi:10.1186/1748-7188-8-9.

\bibitem{Unequal} Rueda L., Bari A., Ngom A. (2008) Clustering Time-Series Gene Expression Data with Unequal Time Intervals. In: Priami C., Dressler F., Akan O.B., Ngom A. (eds) Transactions on Computational Systems Biology X. Lecture Notes in Computer Science, vol 5410. Springer, Berlin, Heidelberg

\bibitem{short_time} Ernst, Jason, Nau, Gerard and Bar-Joseph, Ziv. (2005). Clustering Short Time Series Gene Expression Data. Bioinformatics (Oxford, England). 21 Suppl 1. i159-68. 10.1093/bioinformatics/bti1022. 

\bibitem{Bar_Josep} Ziv Bar-Joseph; Analyzing time series gene expression data, Bioinformatics, Volume 20, Issue 16, 1 November 2004, Pages 2493–2503, https://doi.org/10.1093/bioinformatics/bth283

\bibitem{continous} Ziv Bar-Joseph, Georg K. Gerber, David K. Gifford, Tommi S. Jaakkola, and Itamar Simon. Continuous Representations of Time-Series Gene Expression Data . Journal of Computational Biology. July 2004, 10(3-4): 341-356. https://doi.org/10.1089/10665270360688057

\bibitem{new approach} Bar-Joseph, Ziv \& Gerber, Georg \& K Gifford, David \& S. Jaakkola, Tommi \& Simon, Itamar. (2002). A New Approach to Analyzing Gene Expression Time Series Data. Proceedings of the Annual International Conference on Computational Molecular Biology, RECOMB. 10.1145/565196.565202. 

\bibitem{review paper} Androulakis IP, Yang E, Almon RR. Analysis of Time-Series Gene Expression Data: Methods, Challenges, and Opportunities. Annual review of biomedical engineering. 2007;9:205-228. doi:10.1146/annurev.bioeng.9.060906.151904.

\bibitem{bayesian} Kim S., Imoto S., Miyano S. (2003) Dynamic Bayesian Network and Nonparametric Regression for Nonlinear Modeling of Gene Networks from Time Series Gene Expression Data. In: Priami C. (eds) Computational Methods in Systems Biology. CMSB 2003. Lecture Notes in Computer Science, vol 2602. Springer, Berlin, Heidelberg

\bibitem{svm} J. Ma, S. Perkins, Time-series novelty detection using one-class
support vector machines, in: Proceedings of the International Joint
Conference on Neural Networks, vol. 3, IEEE, 2003, pp. 1741
–
1745

\bibitem{deep learning} X. Qiu, L. Zhang, Y. Ren, P. N. Suganthan, and G. Amaratun
ga,
“Ensemble deep learning for regression and timeseries foreca
sting,” in
Proc. IEEE Symposium on Computational Intelligence and Ens
emble
Learning (CIEL’14)
, Orlando, US, Dec. 2014.

\bibitem{immunology} D. Dasgupta, S. Forrest, Novelty-detection in time series
data using ideas from immunology, Proceedings of the
International  Conference  on  Intelligent  Systems,  Reno,
Nevada, 1996

\bibitem{boltzman} Takashi Kuremoto, Shinsuke Kimura, Kunikazu Kobayashi, Masanao Obayashi,
Time series forecasting using a deep belief network with restricted Boltzmann machines,
Neurocomputing,
Volume 137,
2014,
Pages 47-56,
ISSN 0925-2312,
https://doi.org/10.1016/j.neucom.2013.03.047.

\bibitem{financial} Kyoung-jae Kim,
Financial time series forecasting using support vector machines,
Neurocomputing,
Volume 55, Issues 1–2,
2003,
Pages 307-319,
ISSN 0925-2312,
https://doi.org/10.1016/S0925-2312(03)00372-2.

\bibitem{multiple} Chan, P., Mahoney, M., 2005. Modeling multiple time series for anomaly detection.
In: Proceedings of the Fifth IEEE International Conference on Data Mining,
pp. 90–97

\bibitem{yeast} 
Gasch AP, Spellman PT, Kao CM, et al. Genomic Expression Programs in the Response of Yeast Cells to Environmental Changes. Silver PA, ed. Molecular Biology of the Cell. 2000;11(12):4241-4257.

\bibitem{one_svm} Estimating the support of a high-dimensional distribution Schölkopf, Bernhard, et al. Neural computation 13.7 (2001): 1443-1471.

\bibitem{elliptic} Rousseeuw, P.J., Van Driessen, K. “A fast algorithm for the minimum covariance determinant estimator” Technometrics 41(3), 212 (1999)

\bibitem{isolation} Liu, Fei Tony, Ting, Kai Ming and Zhou, Zhi-Hua. “Isolation forest.” Data Mining, 2008. ICDM‘08. Eighth IEEE International Conference on.

\bibitem{local} Breunig, Kriegel, Ng, and Sander (2000) LOF: identifying density-based local outliers. Proc. ACM SIGMOD

\bibitem{arima} Fang-Mei Tseng, Gwo-Hshiung Tzeng,
A fuzzy seasonal ARIMA model for forecasting,
Fuzzy Sets and Systems,
Volume 126, Issue 3,
2002,
Pages 367-376,
ISSN 0165-0114,
https://doi.org/10.1016/S0165-0114(01)00047-1.

\bibitem{ccycle} 	
Eser P, Demel C, Maier KC, et al. Periodic mRNA synthesis and degradation co‐operate during cell cycle gene expression. Molecular Systems Biology. 2014;10(4):726. doi:10.1002/msb.20140001.

\bibitem{first_dataset}
Cho, R.J., Campbell, M.J., Winzeler, E.A., Steinmetz, L., Conway, A., Wodicka, L., Wolfsberg, T.G., Gabrielian, A.E., Landsman, D., Lockhart, D.J., Davis, R.W.: A genome-wide transcriptional analysis of the mitotic cell cycle. Molecular Cell 2, 65–73 (1998)

\bibitem{second_dataset}
Baranzini, S., Mousavi, P., Rio, J., Caillier, S., Stillman, A., Villoslada, P., Wyatt, M., Comabella, M., Greller, L., Somogyi, R., Montalban, X., Oksenberg, J.: Transcription-based prediction of response to IFN$\beta$ using supervised computational methods. PLoS Biology 3, 166–176 (2005)

\end{thebibliography}